paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
update paper-files

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using kable with additional styling
kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

>>>>

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table2 <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using kable with additional styling
kable(pivoted_table2, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))
